Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-08 sas2015/content/related.tex
tweak

Our approach superficially resembles, but is orthogonal, to context
sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.

>>>>

Our approach superficially resembles, but is orthogonal to, context
sensitivity, including the CPA algorithm~\cite{Agesen:95} and such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.
